---
title: "Urine chemicals by covariates"
author: "Meizhen Yao"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    highlight: tango
    df_print: kable
    fig_caption: yes
    fig_height: 7
    fig_width: 10
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    self_contained: yes
    code_folding: hide
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '6'
header-includes: \usepackage{multirow}
---

  <script language="javascript"> 
    function toggle(num) {
      var ele = document.getElementById("toggleText" + num);
      var text = document.getElementById("displayText" + num);
      if(ele.style.display == "block") {
        ele.style.display = "none";
        text.innerHTML = "show";
      }
      else {
        ele.style.display = "block";
        text.innerHTML = "hide";
      }
   } 
  </script>

<style>
pre {
  white-space: pre !important;
  overflow-x: scroll !important;  
  overflow-y: scroll !important;
  height: auto !important;
  max-height: 80vh !important;
}
</style>

```{r setup, include=FALSE}
options(digits = 4)
knitr::opts_chunk$set(echo = TRUE,tidy=TRUE,cache=F,warning = FALSE)
options(qwraps2_markup = "markdown")

```

```{r,message=FALSE,warning=FALSE,include=FALSE}
library(broom)
library(gtsummary)
library(gt)
library(tidyverse)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(readxl)
library(boot)
library(table1)
library(flextable)
library(plyr)
library(Rcpp)
library(modelr)
library(readr)
library(blme)
library(glmnet)
library(forcats)
library(GGally)

#-------------------------------------------------------load data
Phthalates<-  read_excel("~/Projects/S-PRESTO/input/for paper/chemical_paper/prepared_Phthalates_long_20230317.xlsx")
Pesticides<-  read_excel("~/Projects/S-PRESTO/input/for paper/chemical_paper/prepared_Pesticides_long_20230317.xlsx")


## log transformation

Phthalates <- Phthalates %>% 
              mutate(adjusted_MEP_log=log2(adjusted_MEP), 
                              adjusted_MCPP_log=log2(adjusted_MCPP), 
                              adjusted_MBZP_log=log2(adjusted_MBZP), 
                              adjusted_MBP_log=log2(adjusted_MBP), 
                              adjusted_MIBP_log=log2(adjusted_MIBP), 
                              adjusted_MEHP_log=log2(adjusted_MEHP), 
                              adjusted_MEOHP_log=log2(adjusted_MEOHP),
                              adjusted_MEHHP_log=log2(adjusted_MEHHP), 
                              adjusted_MECPP_log=log2(adjusted_MECPP), 
                              adjusted_MCIOP_log=log2(adjusted_MCIOP), 
                              adjusted_MCINP_log=log2(adjusted_MCINP),  
                              adjusted_MEOHTP_log=log2(adjusted_MEOHTP), 
                              adjusted_MEHHTP_log=log2(adjusted_MEHHTP), 
                              adjusted_MECPTP_log=log2(adjusted_MECPTP))
Pesticides <- Pesticides %>% 
             mutate(adjusted_PBA_log=log2(adjusted_PBA), 
                    adjusted_CIS_DCCA_log=log2(adjusted_CIS_DCCA), 
                    adjusted_TRANS_DCCA_log=log2(adjusted_TRANS_DCCA), 
                    adjusted_PNP_log=log2(adjusted_PNP), 
                    adjusted_TCP_log=log2(adjusted_TCP), 
                    adjusted_DMP_log=log2(adjusted_DMP), 
                    adjusted_DMTP_log=log2(adjusted_DMTP), 
                    adjusted_DMDP_log=log2(adjusted_DMDP), 
                    adjusted_DEP_log=log2(adjusted_DEP), 
                    adjusted_DETP_log=log2(adjusted_DETP), 
                    adjusted_DEDP_log=log2(adjusted_DEDP))

########################################################
### covariates
Phthalates$age_at_recruitment_cat<- factor(Phthalates$age_at_recruitment_cat,
                                           levels=c("Age first tertile","Age second tertile","Age third tertile"))


Phthalates$pcv1_bmi_cat<- factor(Phthalates$pcv1_bmi_cat,
                                      levels=c("Underweight","Healthy weight","Overweight","Obesity"))


Phthalates$Analysis_Batch_recat<- factor(Phthalates$Analysis_Batch_recat)

Phthalates$ethnicity_specified_recat<- factor(Phthalates$ethnicity_specified_recat,
                                             levels=c("Chinese","Malay","Indian"))

Phthalates$pcv1_highest_education_completed_recat<- factor(Phthalates$pcv1_highest_education_completed_recat,
                                           levels=c("University","Primary/Secondary/Post_secondary"))

Phthalates$pcv1_household_income_recat<- factor(Phthalates$pcv1_household_income_recat,
                                           levels=c("$5,696 and below","$5,697 - $10,159","$10,160 and above"))


Phthalates$pcv1_parity_recat<- factor(Phthalates$pcv1_parity_recat,
                                  levels=c("0",">= 1"))

Phthalates$pcv1_smoker<- factor(Phthalates$pcv1_smoker,
                                      levels=c("Never Smoke","Smoker","Ex-smoker"))
                                      
Phthalates$pcv1_ever_drink_alcohol<- factor(Phthalates$pcv1_ever_drink_alcohol,
                                      levels=c("No","Yes"))


Pesticides$age_at_recruitment_cat<- factor(Pesticides$age_at_recruitment_cat,
                                           levels=c("Age first tertile","Age second tertile","Age third tertile"))


Pesticides$pcv1_bmi_cat<- factor(Pesticides$pcv1_bmi_cat,
                                      levels=c("Underweight","Healthy weight","Overweight","Obesity"))


Pesticides$Analysis_Batch_recat<- factor(Pesticides$Analysis_Batch_recat)

Pesticides$ethnicity_specified_recat<- factor(Pesticides$ethnicity_specified_recat,
                                             levels=c("Chinese","Malay","Indian"))

Pesticides$pcv1_highest_education_completed_recat<- factor(Pesticides$pcv1_highest_education_completed_recat,
                                           levels=c("University","Primary/Secondary/Post_secondary"))

Pesticides$pcv1_household_income_recat<- factor(Pesticides$pcv1_household_income_recat,
                                           levels=c("$5,696 and below","$5,697 - $10,159","$10,160 and above"))


Pesticides$pcv1_parity_recat<- factor(Pesticides$pcv1_parity_recat,
                                  levels=c("0",">= 1"))

Pesticides$pcv1_smoker<- factor(Pesticides$pcv1_smoker,
                                      levels=c("Never Smoke","Smoker","Ex-smoker"))
                                      
Pesticides$pcv1_ever_drink_alcohol<- factor(Pesticides$pcv1_ever_drink_alcohol,
                                      levels=c("No","Yes"))



```



# Univariate analysis
```{r}
demo_table <- Phthalates %>%
    filter(Timepoint=="pcv2") %>% 
    select(age_at_recruitment, pcv1_highest_education_completed_recat,ethnicity_specified_recat, pcv1_household_income_recat, pcv1_parity_recat, TotalFish, Fast_food, fruit, vegetable, vegetable_boil, vegetable_SF) %>%
    tbl_summary(missing_text = "Missing", 
                digits = everything() ~ 2
                ) %>%
    bold_labels()

demo_table
```




# Bivariate analysis (pesticides)
## Demographic
### Age
```{r,message=FALSE,warning=FALSE}
pesticides_pcv2_age_table<- Pesticides %>% 
  filter(Timepoint=="pcv2") %>% 
  select(age_at_recruitment_cat, adjusted_PBA_log,adjusted_CIS_DCCA_log,adjusted_TRANS_DCCA_log,adjusted_PNP_log,adjusted_TCP_log,adjusted_DMP_log,adjusted_DMTP_log,adjusted_DMDP_log,adjusted_DEP_log,adjusted_DETP_log,adjusted_DEDP_log) %>% 
  tbl_summary(by=age_at_recruitment_cat,
              missing_text = "Missing") %>% 
                  add_p() %>% 
                  bold_p()%>%  
                  bold_labels() 

pesticides_pgv3_age_table<- Pesticides %>% 
  filter(Timepoint=="pgv3") %>% 
  select(age_at_recruitment_cat, adjusted_PBA_log,adjusted_CIS_DCCA_log,adjusted_TRANS_DCCA_log,adjusted_PNP_log,adjusted_TCP_log,adjusted_DMP_log,adjusted_DMTP_log,adjusted_DMDP_log,adjusted_DEP_log,adjusted_DETP_log,adjusted_DEDP_log) %>% 
  tbl_summary(by=age_at_recruitment_cat,
              missing_text = "Missing") %>% 
                  add_p() %>% 
                  bold_p()%>%  
                  bold_labels() 

pesticides_age_table<- tbl_stack(list(pesticides_pcv2_age_table, pesticides_pgv3_age_table),
                                 group_header = c("pcv2", "pgv3"))%>%
                       as_gt() %>% 
                       tab_style(
                                 style = cell_fill(color = "indianred3"),
                                 locations = cells_body(
                                 columns = p.value,
                                 rows = p.value <=0.05)
                                 )
pesticides_age_table
```

### Education
```{r,message=FALSE,warning=FALSE}
pesticides_pcv2_edu_table<- Pesticides %>% 
  filter(Timepoint=="pcv2") %>% 
  select(pcv1_highest_education_completed_recat, adjusted_PBA_log,adjusted_CIS_DCCA_log,adjusted_TRANS_DCCA_log,adjusted_PNP_log,adjusted_TCP_log,adjusted_DMP_log,adjusted_DMTP_log,adjusted_DMDP_log,adjusted_DEP_log,adjusted_DETP_log,adjusted_DEDP_log) %>% 
  tbl_summary(by=pcv1_highest_education_completed_recat,
              missing_text = "Missing") %>% 
                  add_p() %>% 
                  bold_p()%>%  
                  bold_labels() 

pesticides_pgv3_edu_table<- Pesticides %>% 
  filter(Timepoint=="pgv3") %>% 
  select(pcv1_highest_education_completed_recat, adjusted_PBA_log,adjusted_CIS_DCCA_log,adjusted_TRANS_DCCA_log,adjusted_PNP_log,adjusted_TCP_log,adjusted_DMP_log,adjusted_DMTP_log,adjusted_DMDP_log,adjusted_DEP_log,adjusted_DETP_log,adjusted_DEDP_log) %>% 
  tbl_summary(by=pcv1_highest_education_completed_recat,
              missing_text = "Missing") %>% 
                  add_p() %>% 
                  bold_p()%>%  
                  bold_labels() 

pesticides_edu_table<- tbl_stack(list(pesticides_pcv2_edu_table, pesticides_pgv3_edu_table),
                                 group_header = c("pcv2", "pgv3"))%>%
                       as_gt() %>% 
                       tab_style(
                                 style = cell_fill(color = "indianred3"),
                                 locations = cells_body(
                                 columns = p.value,
                                 rows = p.value <=0.05)
                                 )
pesticides_edu_table
```

### Ethinicity
```{r,message=FALSE,warning=FALSE}
pesticides_pcv2_ethi_table<- Pesticides %>% 
  filter(Timepoint=="pcv2") %>% 
  select(ethnicity_specified_recat, adjusted_PBA_log,adjusted_CIS_DCCA_log,adjusted_TRANS_DCCA_log,adjusted_PNP_log,adjusted_TCP_log,adjusted_DMP_log,adjusted_DMTP_log,adjusted_DMDP_log,adjusted_DEP_log,adjusted_DETP_log,adjusted_DEDP_log) %>% 
  tbl_summary(by=ethnicity_specified_recat,
              missing_text = "Missing") %>% 
                  add_p() %>% 
                  bold_p()%>%  
                  bold_labels() 

pesticides_pgv3_ethi_table<- Pesticides %>% 
  filter(Timepoint=="pgv3") %>% 
  select(ethnicity_specified_recat, adjusted_PBA_log,adjusted_CIS_DCCA_log,adjusted_TRANS_DCCA_log,adjusted_PNP_log,adjusted_TCP_log,adjusted_DMP_log,adjusted_DMTP_log,adjusted_DMDP_log,adjusted_DEP_log,adjusted_DETP_log,adjusted_DEDP_log) %>% 
  tbl_summary(by=ethnicity_specified_recat,
              missing_text = "Missing") %>% 
                  add_p() %>% 
                  bold_p()%>%  
                  bold_labels() 

pesticides_ethi_table<- tbl_stack(list(pesticides_pcv2_ethi_table, pesticides_pgv3_ethi_table),
                                 group_header = c("pcv2", "pgv3"))%>%
                       as_gt() %>% 
                       tab_style(
                                 style = cell_fill(color = "indianred3"),
                                 locations = cells_body(
                                 columns = p.value,
                                 rows = p.value <=0.05)
                                 )
pesticides_ethi_table
```

### Income
```{r,message=FALSE,warning=FALSE}
pesticides_pcv2_income_table<- Pesticides %>% 
  filter(Timepoint=="pcv2") %>% 
  select(pcv1_household_income_recat, adjusted_PBA_log,adjusted_CIS_DCCA_log,adjusted_TRANS_DCCA_log,adjusted_PNP_log,adjusted_TCP_log,adjusted_DMP_log,adjusted_DMTP_log,adjusted_DMDP_log,adjusted_DEP_log,adjusted_DETP_log,adjusted_DEDP_log) %>% 
  tbl_summary(by=pcv1_household_income_recat,
              missing_text = "Missing") %>% 
                  add_p() %>% 
                  bold_p()%>%  
                  bold_labels() 

pesticides_pgv3_income_table<- Pesticides %>% 
  filter(Timepoint=="pgv3") %>% 
  select(pcv1_household_income_recat, adjusted_PBA_log,adjusted_CIS_DCCA_log,adjusted_TRANS_DCCA_log,adjusted_PNP_log,adjusted_TCP_log,adjusted_DMP_log,adjusted_DMTP_log,adjusted_DMDP_log,adjusted_DEP_log,adjusted_DETP_log,adjusted_DEDP_log) %>% 
  tbl_summary(by=pcv1_household_income_recat,
              missing_text = "Missing") %>% 
                  add_p() %>% 
                  bold_p()%>%  
                  bold_labels() 

pesticides_income_table<- tbl_stack(list(pesticides_pcv2_income_table, pesticides_pgv3_income_table),
                                 group_header = c("pcv2", "pgv3"))%>%
                       as_gt() %>% 
                       tab_style(
                                 style = cell_fill(color = "indianred3"),
                                 locations = cells_body(
                                 columns = p.value,
                                 rows = p.value <=0.05)
                                 )
pesticides_income_table
```


### Parity
```{r,message=FALSE,warning=FALSE}
pesticides_pcv2_parity_table<- Pesticides %>% 
  filter(Timepoint=="pcv2") %>% 
  select(pcv1_parity_recat, adjusted_PBA_log,adjusted_CIS_DCCA_log,adjusted_TRANS_DCCA_log,adjusted_PNP_log,adjusted_TCP_log,adjusted_DMP_log,adjusted_DMTP_log,adjusted_DMDP_log,adjusted_DEP_log,adjusted_DETP_log,adjusted_DEDP_log) %>% 
  tbl_summary(by=pcv1_parity_recat,
              missing_text = "Missing") %>% 
                  add_p() %>% 
                  bold_p()%>%  
                  bold_labels() 

pesticides_pgv3_parity_table<- Pesticides %>% 
  filter(Timepoint=="pgv3") %>% 
  select(pcv1_parity_recat, adjusted_PBA_log,adjusted_CIS_DCCA_log,adjusted_TRANS_DCCA_log,adjusted_PNP_log,adjusted_TCP_log,adjusted_DMP_log,adjusted_DMTP_log,adjusted_DMDP_log,adjusted_DEP_log,adjusted_DETP_log,adjusted_DEDP_log) %>% 
  tbl_summary(by=pcv1_parity_recat,
              missing_text = "Missing") %>% 
                  add_p() %>% 
                  bold_p()%>%  
                  bold_labels() 

pesticides_parity_table<- tbl_stack(list(pesticides_pcv2_parity_table, pesticides_pgv3_parity_table),
                                 group_header = c("pcv2", "pgv3"))%>%
                       as_gt() %>% 
                       tab_style(
                                 style = cell_fill(color = "indianred3"),
                                 locations = cells_body(
                                 columns = p.value,
                                 rows = p.value <=0.05)
                                 )
pesticides_parity_table
```


## Dietary factor
```{r,warning=FALSE,message=FALSE}
# specify metal mixture
dietary_Pesticides=names(Pesticides[,c('adjusted_PBA','adjusted_CIS_DCCA','adjusted_TRANS_DCCA','adjusted_PNP','adjusted_TCP','adjusted_DMP','adjusted_DMTP','adjusted_DMDP','adjusted_DEP','adjusted_DETP','adjusted_DEDP',"TotalFish","Fast_food","fruit","vegetable","vegetable_boil","vegetable_SF")])
# mixture_PFAS

library(ggcorrplot)
forcorr = cor(data.frame(Pesticides[,dietary_Pesticides]), method = "spearman")


library(corrplot)
corrplot(forcorr, 
         method="color" ,
         col = colorRampPalette(c("steelblue", "white", "darkred"))(100),cl.lim=c(0,1),
         type="upper",
         tl.pos = 'tp',
         tl.srt=30,
         tl.col = "black",
         ) 
corrplot(forcorr, 
         method="number", 
         type="lower", 
         col = 'black', 
         tl.pos = 'n',
         cl.pos = 'n',
         add=TRUE
         )  



dev.off()

```

























