---
title: "S-PRESTO Phthalates determinants Multivariable regressions"
author: "Meizhen Yao"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    highlight: tango
    df_print: paged
    fig_caption: yes
    fig_height: 7
    fig_width: 10
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    self_contained: yes
    code_folding: hide
    toc_depth: 6
header-includes: \usepackage{multirow}
---

<style type="text/css">
body{
  /*font-family: Helvetica;*/
  font-size: 12pt;
}
</style>


```{r setup, include=FALSE}
options(digits = 4)
knitr::opts_chunk$set(echo = TRUE,tidy=TRUE,cache=F,warning = FALSE)
# suppress warning messages for final rendering
old.warn <- getOption("warn")
options(qwraps2_markup = "markdown")

```


```{r, message=FALSE,warning=FALSE}
# load packages
library(broom)
library(gtsummary)
library(gt)
library(tidyverse)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(readxl)
library(boot)
library(table1)
library(flextable)
library(plyr)
library(Rcpp)
library(modelr)
library(readr)
library(gWQS)
library(broom.mixed)
library(yaml)
library(rmarkdown)
library(officer)
library(scales)
library(lme4)

# import data (change the path to the location where you save the dataset)
Phthalates<- read_excel("~/Projects/S-PRESTO/input/for paper/chemical_paper/prepared_Phthalates_long_20230317.xlsx")

## log transformation
phtha_log <- Phthalates %>% 
              mutate(adjusted_MEP_log=log2(adjusted_MEP), 
                              adjusted_MCPP_log=log2(adjusted_MCPP), 
                              adjusted_MBZP_log=log2(adjusted_MBZP), 
                              adjusted_MBP_log=log2(adjusted_MBP), 
                              adjusted_MIBP_log=log2(adjusted_MIBP), 
                              adjusted_MEHP_log=log2(adjusted_MEHP), 
                              adjusted_MEOHP_log=log2(adjusted_MEOHP),
                              adjusted_MEHHP_log=log2(adjusted_MEHHP), 
                              adjusted_MECPP_log=log2(adjusted_MECPP), 
                              adjusted_MCIOP_log=log2(adjusted_MCIOP), 
                              adjusted_MCINP_log=log2(adjusted_MCINP),  
                              adjusted_MEOHTP_log=log2(adjusted_MEOHTP), 
                              adjusted_MEHHTP_log=log2(adjusted_MEHHTP), 
                              adjusted_MECPTP_log=log2(adjusted_MECPTP),
            TotalFish_sc = (TotalFish - mean(TotalFish))/sd(TotalFish),
            Fast_food_sc = (Fast_food - mean(Fast_food))/sd(Fast_food),
            fruit_sc = (fruit - mean(fruit))/sd(fruit),
            vegetable_sc = (vegetable - mean(vegetable))/sd(vegetable),
            vegetable_boil_sc = (vegetable_boil - mean(vegetable_boil))/sd(vegetable_boil),
            vegetable_SF_sc = (vegetable_SF - mean(vegetable_SF))/sd(vegetable_SF),
            Styrofoam_boxes_freq_mean_sc = (Styrofoam_boxes_freq_mean - mean(Styrofoam_boxes_freq_mean))/sd(Styrofoam_boxes_freq_mean),
            Plastic_boxes_freq_mean_sc = (Plastic_boxes_freq_mean - mean(Plastic_boxes_freq_mean))/sd(Plastic_boxes_freq_mean),
            Canned_freq_mean_sc = (Canned_freq_mean - mean(Canned_freq_mean))/sd(Canned_freq_mean))


### covariates
phtha_log$ethnicity_specified_recat<- factor(phtha_log$ethnicity_specified_recat,
                                            levels = c("Chinese", "Indian/Malay"))

phtha_log$pcv1_highest_education_completed_recat<- factor(phtha_log$pcv1_highest_education_completed_recat,
                                           levels=c("University","Primary/Secondary/Post_secondary"))

phtha_log$pcv1_household_income_recat<- factor(phtha_log$pcv1_household_income_recat,
                                           levels=c("$6,376 and below","$6,377 - $11,293","$11,294 and above"))


phtha_log$pcv1_parity_recat<- factor(phtha_log$pcv1_parity_recat,
                                  levels=c("0",">= 1"))



phtha_log$age_at_recruitment_cat <- factor(phtha_log$age_at_recruitment_cat,
                                           levels=c("Age first tertile","Age second tertile","Age third tertile"))

phtha_log$Styrofoam_boxes<- factor(phtha_log$Styrofoam_boxes,
                                        levels = c("No", "Yes"))
phtha_log$Plastic_boxes<- factor(phtha_log$Plastic_boxes,
                                        levels = c("No", "Yes"))
phtha_log$Canned<- factor(phtha_log$Canned,
                               levels = c("No", "Yes"))


## phthalates information
phtha<- c('adjusted_MEP_log','adjusted_MCPP_log','adjusted_MBZP_log','adjusted_MBP_log','adjusted_MIBP_log','adjusted_MEHP_log','adjusted_MEOHP_log','adjusted_MEHHP_log','adjusted_MECPP_log','adjusted_MCIOP_log','adjusted_MCINP_log','adjusted_MEOHTP_log','adjusted_MEHHTP_log','adjusted_MECPTP_log')

str(phtha_log)

phtha_parent<- c("DEP", "DBP", "BBzP", "DBP", "DiBP", "DEHP", "DEHP", "DEHP", "DEHP", "DiNP", "DiDP", "DEHTP", "DEHTP","DEHTP")
phtha_group<- c("LMWPs", "HMWPs", "HMWPs", "LMWPs", "LMWPs", "HMWPs", "HMWPs", "HMWPs", "HMWPs", "HMWPs", "HMWPs", "HMWPs", "HMWPs", "HMWPs")

phtha_info<- data.frame(phtha,
                        phtha_parent,
                        phtha_group)


```

# Linear Mixed-effect models
## model1: sociodemographic factors
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

####### extract results
# write_csv(phtha_mixreg1_coefs_data, "C:/Users/yaom03/OneDrive - The Mount Sinai Hospital/Documents/Projects/S-PRESTO/code/R/chemical & covariates/plot_data/phtha_model1_raw.csv")


```



## model2: one dietary factor + sociodemographic factors
### Total fish
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ TotalFish_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel


######## extract results
fish<- phtha_mixreg1_coefs_data %>% 
       filter(term == "TotalFish_sc")

```


### Fast food
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ Fast_food_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

######## extract results
fast_food<- phtha_mixreg1_coefs_data %>% 
       filter(term == "Fast_food_sc")
```

### Fruit
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ fruit_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

######## extract results
fruit<- phtha_mixreg1_coefs_data %>% 
        filter(term == "fruit_sc")
```


### Vegetable
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ vegetable_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

######## extract results
vegetable<- phtha_mixreg1_coefs_data %>% 
        filter(term == "vegetable_sc")

```

### Vegetable boil
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ vegetable_boil_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel


######## extract results
vegetable_boil<- phtha_mixreg1_coefs_data %>% 
            filter(term == "vegetable_boil_sc")
```

### Vegetable stir fried
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ vegetable_SF_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

######## extract results
vegetable_SF<- phtha_mixreg1_coefs_data %>% 
            filter(term == "vegetable_SF_sc")
```

### Styrofoam boxes
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ Styrofoam_boxes + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

######## extract results
Styrofoam_boxes<- phtha_mixreg1_coefs_data %>% 
            filter(term == "Styrofoam_boxesYes")
```

### Styrofoam boxes mean frequency
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ Styrofoam_boxes_freq_mean_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

######## extract results
Styrofoam_boxes_freq<- phtha_mixreg1_coefs_data %>% 
            filter(term == "Styrofoam_boxes_freq_mean_sc")
```

### Plastic boxes
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ Plastic_boxes + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

######## extract results
Plastic_boxes<- phtha_mixreg1_coefs_data %>% 
            filter(term == "Plastic_boxesYes")
```


### Plastic boxes mean frequency
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ Plastic_boxes_freq_mean_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

######## extract results
Plastic_boxes_freq<- phtha_mixreg1_coefs_data %>% 
            filter(term == "Plastic_boxes_freq_mean_sc")

```

### Canned
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ Canned + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

######## extract results
Canned<- phtha_mixreg1_coefs_data %>% 
            filter(term == "CannedYes")
```


### Canned mean frequency
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_mixreg1 <-
  lapply(phtha, function(x){
    
    lmer(formula = substitute(i ~ Canned_freq_mean_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat+ (1 | Subject_ID), 
                           list(i = as.name(x))),
      data = phtha_log)
    
  })

## extract coefficients with confidence interval
phtha_mixreg1_coefs <- lapply(phtha_mixreg1, tidy, conf.int = T)
names(phtha_mixreg1_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_mixreg1_coefs_data1 <- bind_rows(phtha_mixreg1_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_mixreg1_coefs_data <- phtha_mixreg1_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_mixreg1_coefs_data$phtha_parent<- factor(phtha_mixreg1_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_mixreg1_coefs_data<- phtha_mixreg1_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_mixreg1_coefs_data$sig<- ifelse(phtha_mixreg1_coefs_data$conf.low >0 & phtha_mixreg1_coefs_data$conf.high >0 | phtha_mixreg1_coefs_data$conf.low <0 & phtha_mixreg1_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_mixreg1_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel


######## extract results
Canned_freq<- phtha_mixreg1_coefs_data %>% 
            filter(term == "Canned_freq_mean_sc")

```

```{r}
phtha_model2<- rbind(fish,
                    fast_food,
                    fruit,
                    vegetable,
                    vegetable_boil,
                    vegetable_SF,
                    Styrofoam_boxes,
                    Styrofoam_boxes_freq,
                    Plastic_boxes,
                    Plastic_boxes_freq,
                    Canned,
                    Canned_freq)


######## extract results
# write_csv(phtha_model2, "C:/Users/yaom03/OneDrive - The Mount Sinai Hospital/Documents/Projects/S-PRESTO/code/R/chemical & covariates/plot_data/phtha_model2_raw.csv")




```


# Linear regression models
## pcv2
```{r}
phtha_log_pcv2<- phtha_log %>% 
                filter(Timepoint=="pcv2")
```

### model1: sociodemographic factors
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```

### model2: one dietary factor + sociodemographic factors
#### Total fish
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ TotalFish_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```


#### Fast food
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Fast_food_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel
```

#### Fruit
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ fruit_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```


#### Vegetable
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ vegetable_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```

#### Vegetable boil
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ vegetable_boil_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```

#### Vegetable stir fried
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ vegetable_SF_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```

#### Styrofoam boxes
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Styrofoam_boxes + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```


#### Styrofoam boxes mean frequency
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Styrofoam_boxes_freq_mean + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```


#### Plastic boxes
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Plastic_boxes + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```

#### Plastic boxes mean frequency
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Plastic_boxes_freq_mean + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```


#### Canned
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Canned + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```

#### Canned mean frequency
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pcv2 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Canned_freq_mean + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pcv2,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pcv2_coefs <- lapply(phtha_multireg1_pcv2, tidy, conf.int = T)
names(phtha_multireg1_pcv2_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pcv2_coefs_data1 <- bind_rows(phtha_multireg1_pcv2_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pcv2_coefs_data <- phtha_multireg1_pcv2_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pcv2_coefs_data$phtha_parent<- factor(phtha_multireg1_pcv2_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pcv2_coefs_data<- phtha_multireg1_pcv2_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pcv2_coefs_data$sig<- ifelse(phtha_multireg1_pcv2_coefs_data$conf.low >0 & phtha_multireg1_pcv2_coefs_data$conf.high >0 | phtha_multireg1_pcv2_coefs_data$conf.low <0 & phtha_multireg1_pcv2_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pcv2_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```




## pgv3
```{r}
phtha_log_pgv3<- phtha_log %>% 
                filter(Timepoint=="pgv3")
```

### model1: sociodemographic factors
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```

### model2: one dietary factor + sociodemographic factors
#### Total fish
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ TotalFish_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel
```


#### Fast food
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Fast_food_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```

#### Fruit
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ fruit_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```


#### Vegetable
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ vegetable_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```

#### Vegetable boil
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ vegetable_boil_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel

```

#### Vegetable stir fried
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ vegetable_SF_sc + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel
```

#### Styrofoam boxes
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Styrofoam_boxes + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel
```

#### Styrofoam boxes mean frequency
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Styrofoam_boxes_freq_mean + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel
```

#### Plastic boxes
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Plastic_boxes + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel
```

#### Plastic boxes mean frequency
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Plastic_boxes_freq_mean + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel
```

#### Canned
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Canned + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel
```


#### Canned mean frequency
```{r, message=FALSE,warning=FALSE}

## Fit the models
phtha_multireg1_pgv3 <-
  lapply(phtha, function(x){
    
    glm(formula = substitute(i ~ Canned_freq_mean + ethnicity_specified_recat + age_at_recruitment_cat + pcv1_highest_education_completed_recat + pcv1_household_income_recat +pcv1_parity_recat, 
                           list(i = as.name(x))),
      data = phtha_log_pgv3,
      family = gaussian())
    
  })

## extract coefficients with confidence interval
phtha_multireg1_pgv3_coefs <- lapply(phtha_multireg1_pgv3, tidy, conf.int = T)
names(phtha_multireg1_pgv3_coefs) <- phtha

## combine all lists into one big table
## gives estimates and CI for biomarkers and variables
phtha_multireg1_pgv3_coefs_data1 <- bind_rows(phtha_multireg1_pgv3_coefs, .id = "phtha")


## subset estimates and CI for _only the biomarkers_
phtha_multireg1_pgv3_coefs_data <- phtha_multireg1_pgv3_coefs_data1 %>% 
                           filter(term != "(Intercept)" & term !=  "sd__(Intercept)" & term !=  "sd__Observation") %>% 
                           mutate(Estimate = round(estimate, 3),
                                  conf.low = round(conf.low, 3),
                                  conf.high = round(conf.high, 3)) %>% 
                           select(phtha, term, Estimate, conf.low, conf.high) %>% 
                           inner_join(phtha_info, by="phtha") 

phtha_multireg1_pgv3_coefs_data$phtha_parent<- factor(phtha_multireg1_pgv3_coefs_data$phtha_parent,
                          levels = c("DEP", "DiBP", "DBP", "DEHTP", "DEHP", "DiNP", "BBzP", "DiDP"))
phtha_multireg1_pgv3_coefs_data<- phtha_multireg1_pgv3_coefs_data %>% 
                           arrange(phtha_parent, desc(phtha_group))

phtha_multireg1_pgv3_coefs_data$sig<- ifelse(phtha_multireg1_pgv3_coefs_data$conf.low >0 & phtha_multireg1_pgv3_coefs_data$conf.high >0 | phtha_multireg1_pgv3_coefs_data$conf.low <0 & phtha_multireg1_pgv3_coefs_data$conf.high <0, "*", NA )

## put result into one table
tabel<- flextable(as_grouped_data(phtha_multireg1_pgv3_coefs_data, groups = c("phtha_group","phtha_parent","phtha"))) %>%          
        color(~sig == "*", ~conf.low, color = "red")%>% 
        color(~sig == "*", ~conf.high, color = "red")%>%
        theme_box() 
        

tabel
```




<!-- ## combine datasets -->
<!-- ```{r, message=FALSE,warning=FALSE} -->
<!-- phtha_multireg1_coefs_data<- rbind(phtha_multireg1_pcv2_coefs_data, phtha_multireg1_pgv3_coefs_data) -->

<!-- write_xlsx(phtha_multireg1_coefs_data, "~/Projects/S-PRESTO/code/R/Tomer/manuscript figure/input/figure4_data_raw_08122022.xlsx") -->
<!-- ``` -->








